### 2015-01-19 src/methodology.Rnw
update

\subsection{Sampling Criteria}

We used several different sampling criteria that has been mentioned in the
literature, For each sampling criteria, we sampled mutants on a decreasing
power scale, sampling \textit{1/2, 1/4, 1/8, 1/16, 1/32, 1/64} of the total
mutants.

\subsubsection{x\% selection}
The simplest sampling approach consisted of using x\% selection as suggested by
Budd~\cite{budd1980mutation}. In this criteria, we choose a specific
fraction of the complete set of mutants. This criteria also serves as a
baseline for verifying the effectiveness of other criteria.

\subsubsection{x\% selection per operator}
This strategy, first suggested by Wong et al.~\cite{wong1995reducing} samples an equal percentage
of mutants from each operator.

\subsubsection{Sampling over program elements}
Following the suggestion of Zhang et al.~\cite{zhang2013ase}, we
extended x\% selection criteria to sample from within different program
elements.  We sampled in increasing order of scope,
--- \textit{line}, \textit{method} and \textit{class} (\textit{project}
scope is just x\% selection).

>>>>

\subsection{Sampling Criteria}
We used several different sampling criteria that has been mentioned in the
literature, For each sampling criteria, we sampled mutants on a decreasing
power scale, sampling $\frac{1}{2}$, $\frac{1}{4}$, $\frac{1}{8}$,
$\frac{1}{16}$, $\frac{1}{32}$, $\frac{1}{64}$ of the total mutants.

\subsubsection{Uniform random sampling}
The simplest sampling approach consisted of using x\% selection as suggested
by Budd~\cite{budd1980mutation}. In this criteria, we choose a specific
fraction of the complete set of mutants. This criteria also serves as a
baseline for verifying the effectiveness of other criteria.

\subsubsection{Stratified random sampling over mutation operators}
This strategy, first suggested by Wong et al.~\cite{wong1995reducing}
samples an equal percentage of mutants from each operator. While Wong seems
to treat this as same as x\% selection, without giving any further
justification as to why it was used instead, we note that this sampling is
subtly different from pure random sampling in that it provides a stratified
sampling based on mutation operators.

\subsubsection{Stratified random sampling over program elements}
Following the suggestion of Zhang et al.~\cite{zhang2013ase}, we extended
x\% selection criteria to sample from within different program elements.
We sampled in increasing order of scope, --- \textit{line}, \textit{method}
and \textit{class} (\textit{project} scope is just x\% selection).
